Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-28 supp/supp.qmd
Update to prevent messages
Added Losia's code in for gender analysis

```{r, setup}
#| label: setup

@@

>>>>

```{r, setup}
#| label: setup
#| echo: false
#| include: false

@@

 ##### ADDED BY ML"  
install.packages("gender")
install.packages("genderdata")
library(gender)

## testing - delete thi later
#gender(c("Madison", "Hillary"), years = 2000, method = "ssa")
#gender(c("Madison", "Hillary"), method = "genderize") #works ok until limit of 100 is reached
#gender(data3$submitting_author_firstname, method = "genderize") #works ok until limit of 100 is reached

# data3 <-  data2[1:100, ] #subset for testing
# gender(data3$submitting_author_firstname) -> data3_genders
# dim(data3_genders) #83 names assigned
## EDN testing

# Get gender using all unique first names from the data set
data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
dim(data_genders) #514 assigned
#names(data_genders)

# Merge with main data frame
#unique(data_genders$name)
data_genders <- rename(data_genders, submitting_author_firstname = name)
data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
#names(data3)
table(is.na(data3$proportion_male)) #157 missing

# Plot probabilities of gender assignment
ggplot(data3, aes(x = `proportion_male`)) +
  geom_histogram(fill = "grey", color = "black") +
  labs(x = "gender assignment probability (male)", y = "Number of preprints") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

table(data3$proportion_male > 0.05 & data3$proportion_male < 0.95) #84 names bit unsure

# Pull out records missing names
#data3[is.na(data3$proportion_male), c("submitting_author", "submitting_author_country") ] #157 missing
#data3[is.na(data3$proportion_male) == FALSE & data3$proportion_male > 0.05 & data3$proportion_male < 0.95, c("submitting_author", "submitting_author_country") ] # 84 missing a bit unsure

#transliterate the non-ASCII characters using stringi package, e.g.: #stri_trans_general("Zażółć gęślą jaźń", "Latin-ASCII")
data3$submitting_author_ASCII <- stringi::stri_trans_general(data3$submitting_author, "Latin-ASCII")

data3 %>% 
  filter(is.na(data3$proportion_male) == TRUE | (proportion_male > 0.05 & proportion_male < 0.95)) %>% dplyr::select(submitting_author_ASCII, submitting_author, submitting_author_country, preprint_title, gender) %>% 
  write.csv(file = here("data", "final_data3_fillin.csv")) #used to manually check and fill in gender data - then saved as final_data3_fillin_ML.csv

# Load updated data	subset
data3_update <- read_csv(here("data", "final_data3_fillin_ML.csv"))
dim(data3_update)
names(data3_update)

data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
#table(data4$gender.x, useNA = "always")
#table(data4$gender.y, useNA = "always")
data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
data4 <- rename(data4, gender = gender.x)
table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship
